Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-28 public/paper/pyg4ometry.tex
Small fixes

# structure 
wl = g4.LogicalVolume(wb, wm, "wl", reg)
bl = g4.LogicalVolume(b, bm, "b", reg)
bp1 = g4.PhysicalVolume([0,0,0],[0,0,0], 
                        bl, "b_pv1", wl) 
bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
                        bl, "b_pv2", wl)  
bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0], 
                        bl, "b_pv3", wl)

@@

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
\caption{FLUKA input with an AST.}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

\section{CAD to GDML conversion }
STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
and visualisation attributes.

@@

>>>>

# structure 
wl = g4.LogicalVolume(wb, wm, "wl", reg)
bl = g4.LogicalVolume(b, bm, "b", reg)
bp1 = g4.PhysicalVolume([0,0,0],
                        [0,0,0], 
                        bl, "b_pv1", wl) 
bp2 = g4.PhysicalVolume([0,0,0],
                        [-2*bx,0,0], 
                        bl, "b_pv2", wl)  
bp3 = g4.PhysicalVolume([0,0,0],
                        [2*bx,0,0], 
                        bl, "b_pv3", wl)

@@

\subsection{Discussion}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, a) 
the original FLUKA geometry displayed in FLAIR, b) the GDML geometry 
viewed in pyg4ometry. The example is a Faraday cup used to capture 
and measure accelerator beam charge}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

\section{CAD to GDML conversion }
STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
and visualisation attributes must be performed by the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
for RT codes.

@@

\begin{enumerate}
\item Graphical front end viewer
\item C++ output
\item CAD BREP to FLUKA converter (a la McCAD) 
\item Integration of other tools (DAGMC) 
\item Far from perfect conversions. 
\end{enumerate}
